---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# buzz

<!-- badges: start -->
<!-- [![R-CMD-check](https://github.com/rsquaredacademy/buzz/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/rsquaredacademy/buzz/actions/workflows/R-CMD-check.yaml) -->
<!-- badges: end -->

Easily create alerts, notifications and tooltips in Shiny.

## Installation

You can install the development version of buzz from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rsquaredacademy/buzz")
```

## Usage

To use alerts or noticiat from **buzz** in your Shiny application, follow the below steps:

- Include the dependencies in the **UI** part of the app using the appropriate
`use*` functions (`useToast()` in the below example).
- Include the corresponding rendering function in the **Server** part of the 
app (`toast()` in the below example).

### Example

```{r example, eval=FALSE}
library(shiny)
library(buzz)

ui <- fluidPage(

  useBootBox(), # include dependencies
  actionButton(inputId = "notify",
               label   = "Show Notification")

)

server <- function(input, output, session) {

  observeEvent(input$pnotify, {
    bootBox(class = "rubberBand") # display the alert
  })
}

shinyApp(ui, server)
```

The below table displays the dependency and rendering functions along with references:

| Index | Dependency      | Render              | Reference                                                                   |
| ------| -------------   | -------------       | -------------                                                               |
| 1     | `useAlertify()` | `alertify_alert()`  | [Alertify](https://github.com/MohammadYounes/AlertifyJS)                    |
| 2     | `useAlertify()` | `alertify_notify()` | [Alertify](https://github.com/MohammadYounes/AlertifyJS)                    |
| 3     | `useBootBox()`  | `bootBox()`         | [BootBox](https://github.com/makeusabrew/bootbox)                           |
| 4     | `useMicroTip()` | `microTip()`        | [MicroTip](https://github.com/ghosh/microtip)                               |
| 5     | `useNS()`       | `notice()`          | [Notification Styles](https://tympanus.net/Development/NotificationStyles/) |
| 6     | `useNotify()`   | `notify()`          | [PNotify](https://github.com/sciactive/pnotify)                             |
| 7     | `useTingle()`   | `tingle()`          | [Tingle](https://github.com/robinparisi/tingle)                             |
| 8     | `useToast()`    | `toast()`           | [iziToast](https://github.com/marcelodolza/iziToast)                        |


## Getting Help

If you encounter a bug, please file a minimal reproducible example using 
[reprex](https://reprex.tidyverse.org/index.html) on github. For questions and clarifications, 
use [StackOverflow](https://stackoverflow.com/).

## Code of Conduct

Please note that the buzz project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
